%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Professional Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

\cventry
{Center for AI and Robot Autonomy (CARA)}
{Director and President}
{Los Angeles, CA}
{Mar 2021 - Present}
{
\begin{cvitems}
\item Define updated mission and vision statements, seek alternative funding, and file paperwork to maintain 501(c)(3) status.
\end{cvitems}
}

\cventry
{Center for AI and Robot Autonomy (CARA)}
{Robotics Research Engineer Intern}
{Los Angeles, CA}
{Jun 2018 - Mar 2020}
{
\begin{cvitems}
\item Worked on representation learning project to couple vision and language (details under UCLA Graduate Student Researcher).
\end{cvitems}
}

\cventry
{Air Force Research Lab (AFRL)}
{Undergraduate Researcher}
{Dayton, OH}
{May 2014 - Sep 2015}
{
\begin{cvitems}
\item Conducted Declarative Memory (semantic knowledge retrieval system) research for the ACT-R cognitive architecture.
\item Architected a new declarative memory system using CUDA, thread pools, parsers, inter-process communication (IPC).
\item Continued project work between summers as undergrad thesis research.
\item \underline{Result}: Parallelized declarative retrievals; yielded a 100x speedup over the fastest existing implementation.
\end{cvitems}
}

\cventry
{Aviation Department, Garmin International}
{Software Engineering Intern}
{Olathe, KS}
{May 2013 - Aug 2013}
{
\begin{cvitems}
\item Automated the testing process for small craft airplane ACARS systems that send timed status messages to ground stations.
\item Reduced testing time by 40\% and saved hundreds of vendor certification testing hours by optimizing simulation timing protocols and adhering to FAA safety standards.
\end{cvitems}
}

\end{cventries}